---
title: "Using litsearchR"
author: "Tania L.G. Maxwell"
date: "1/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document tracks the literature search used to acquire the global C 

## Setup

```{r}
library(remotes)

#download github repro
install_github("elizagrames/litsearchr", ref="main")
library(litsearchr)
```

First step is the naive search for studies with soil carbon data in tidal marshes or salt marshes. 

Guidelines for writing a naive search (from Grames et al. 2019 S1)

*1. Identify your research question:*

What are the soil carbon stocks and carbon sequestration rates in tidal (salt) marshes at the global scale? 

*2. Identify your concept groups (population more broadly as the study system, intervention as the predictor variables, and outcome as the response variables):*

Population/study system = tidal (salt) marshes

Intervention/predictor variables = what we are looking for

Outcome = soil carbon stocks and/or sequestration rates

*3. Use your prior knowledge, or consult with colleagues or experts in your field to generate an initial list of search terms that fit in your concept groups.*

We are interested in soil carbon, but we should include both inorganic and organic carbon, as well as specify if we want soil carbon stocks or sequestration. 

*4. Combine your concept groups into a search string.*

```
      (("soil C" OR "soil carbon" OR "soil inorganic carbon" OR "soil organic carbon") OR
      ("soil carbon sequestrat*" OR "soil carbon stabiliz*" OR "soil carbon stock*"))
      
      AND ("tidal marsh*" OR "salt marsh*" OR saltmarsh*)
```

*5. Assess how discrete your search is and modify as needed.* Generally speaking, if you get more than 700 for a narrowly defined question or more than 1500 for a broader question, you are not being precise enough

### Import native search
```{r}
BBWO_import 
```





## Adding additional recent papers

Once the final literature search has been completed, additional searches will be conduted every (x) months to add new data to the dataset

- note: how can we automatize this process? 
